Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-11-13 paper/ms.tex
new methodology section

Some theoretical attempts to solve this problem using an  ab-initio
approach. They start from the DM halo population to infer the
intrinsic star formation rates and \ly a luminosities. From these
values they estimate the amount of \ly photons that
escape each galaxy and compute the observed luminosity for each
galaxy. These models can predict different observables including: the
luminosity function, correlation function and the equivalent width
distributions. Such modelling has been implemented in semi-analytic
models \citep{Garel2012,Orsi2012, Solre2012} and  full N-body
hydrodynamical simulations \citep{Laursen2007, Dayal2009,
  ForeroRomero2011, Yajima2012}.

However, there are many uncertain steps in these calculations. The
usual ones are the astrophysical processes describing star formation in galactic
populations. But the dominant uncertainty is estimating the
fraction of \ly photons that escape the galaxy, a number known as the escape
fraction. Given the resonant nature of the \ly line, the escape
fraction is sensitive to  the density, temperature, topology and
kinematics of the neutral Hydrogen in the interstellar medium
(ISM), besides the amount of dust that absorb the \ly photons. The
complex radiative transfer of \ly photons in the ISM requires Monte
Carlo simulations to be solved. Until now it has been dificult to
achieve a consensus on the expected value for the \ly escape fraction
in high redshift galaxies
\citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.

A different approach to infer the typical mass of halos hosting
LAEs is based on clustering information. This method uses the fact
that in CDM cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo 
mass. Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010}. In these
studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
the conclusions derived on the halo host mass do not delve too deeply
into the possible impact of cosmic variance.

Recently \cite{Yamada2012} observed a wide area of $2.4$ deg$^{2}$
under homogeneous instrumental and data reduction conditions. This data
set is constructed from 12 different sub-fields. This large and
homogeneous data-set allows us to use clustering statistics and cosmic
variance to constraint the mass and occupation fraction of halos hosting
LAEs.

Our method first populates DM halos in cosmological simulations with
LAEs. We only consider whether a DM can host a detectable LAE or not
without predicting a \ly  luminosity. This is constructed to bypass
all the physical uncertainties involved in the estimation of observed
\ly luminosities.  Once we have the mock LAE catalogs, we compare them
against the statistics on the number density distribution derived from the
observations over the 12 fields of \cite{Yamada2012}. Additionally, we
use measurements of the angular correlation function to improve these
constraints. This method allows us to find the preferred mass range of
DM halos hosting these galaxies and its occupation fraction.

@@

Our method is based on the comparison of observations and mock
catalogs. We use two different kinds of statistics to perform the
comparison: (i) the distribution of the surface number density
across fields and (ii) the angular correlation function measured in
some fields.

In the next subsections we describe in detail the four key
elements of this work-flow. First, we present the observations we take
as a benchmark. Second, we describe the main characteristics of the
N-body simulation and the halo catalogs we use. Third, we recount the
important parameters of the simplified model that we use to populate
the halo catalogs with LAEs. Finally we describe some of the
statistical tests we adopt to compare observations and mocks.

@@

The first observational constraint we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey
conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
which has a field of view covering $34\times 27$ arc-min, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
an observed equivalent width, in the observer frame, larger than $190$
\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
sub-fields,  this corresponds to average surface number density of
$0.20\pm 0.01$ arcmin$^{-2}$.

@@

\begin{enumerate}
\item The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
field has been known to harbor a region with a large density excess of
galaxies. {\bf The first sub-field of is taken around the same region
  observed in \cite{Hayashino2004} } as it is reported  by as by
\cite{Yamada2012} in section $2.1$.

@@

\item The third  field si the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
$196$ LAEs (1 sub-field), and

@@

{\bf A secondary benchmark is the angular correlation function
(ACF). \cite{Yamada2012} does not report an ACF measurement for
  the entire field. Instead we use the results by
  \cite{Hayashino2004} who has reported the ACF in the SSA22 region,
  including its densest subfield. In adition to Hayashino's ACF we use
  as a matter of comparison the ACF reported by
  \cite{Ouchi2008}. This ACF is computer over an observed field of 1
  deg$^2$ over the SXDS field.}

{\bf There are some differences between \cite{Ouchi2008} observations
  and those by \cite{Yamada2012}. The details in the color selection,
  corresponding limiting luminosities and EW thresholds are different
  in these references. The average LAEs number density inferred by
  \cite{Hayashino2004} is   $0.37$ arcmin$^{-2}$, which is $15\%$
  lower than the new measurement by \cite{Yamada2012}. In the case of
  \cite{Ouchi2008} the number density is $0.10$ arcmin$^{-2}$, which
  is $\sim 50\%$ higher than the value inferred by \cite{Yamada2012}
  for a portion of the same region.}

@@

{\bf The field SSA22 has been known to harbor a significant
  galaxy overdensity. \cite{Yamada2012} estimates that the densest
  subfield is likely to be a rare density peak with $3-4\sigma$
  significance on the scale of $\sim 60$\hMpc.}

{\bf Excluding that high density sub-field in SSA22, all the fields
  are average with a similar number density as the blank fields
  rare. The left panel in Figure \ref{fig:halos} shows the integrated distribution of LAEs number density in all the fields reported in
  \cite{Yamada2012}. It is evident that there is only one sub-field that
  stands out as an outlier in the distribution (it corresponds to the
  densest field in SSA22). All the other fields form a continous
  distribution in number density.}

{\bf Therefore, using the whole SSA22 region as a benchmark in the
  number density distribution does not impose any bias. However, on
  has to  keep in mind that is not plausible that the full number
  density distribution from a simulation will include a very dense
  field. The statistical test we perform to compare mock distributions against
  observations does not require such a perfect match.

We will not
  require the presence of such field to judge a mock distribution as
  successful. In terms of the ACF the results that include the densest
  field in SSA22 \citep{Hayashino2004} are consistent, within the
  uncertainties, with the results of other fields \citep{Ouchi2008}.}

{\bf Finally, two very different number densities in LBGs versus LAEs evidences
  that the two populations have different biases. In a $\Lambda$ CDM
  cosmology this implies that LAEs are, on average, hosted by halos
  less massive than those hosting LBGs. The interpretation of how rare
  is this subfield in terms of the number densities of dark matter
  halos has to assume a defined model for galaxy formation;
  i.e. defining the link between halo mass, star formation rate, \ly
  luminosity and \ly escape fraction.}

{\bf The purpose of our work is to avoid any loose of generality by
  assuming a defined halo-LAE connection and instead explore all the
  possible halo populations to host LAEs.}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
  method. The larger panel shows $7$ mock
  fields together mimicking the SSA22 region. The intermediate panel
  shows $3$ mock fields corresponding to the SXDS region. The lower
  panels represent the SDF and GOODS-North fields. The same model has
  another 14 associated mock surveys build from different regions in
  the simulation, but constructed following the same pattern in the
  {\texttt{match}} method.}
\end{center} 
\end{figure*}

We assume that a dark matter halo can only host one
detectable LAE at most.  There are three parameters that
decide whether a halo host a LAE: the lower and upper bounds for the
mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
must keep in mind that the physical interpretation of the occupation
fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
forming galaxy in a halo and its detectability as a LAE.  We do not
perform a explicit modeling for LAE detectability. Our model does not
assign a luminosity or escape fraction to each LAE.  We are only
interested in constraining the halo mass range hosting detectable LAEs
under the conditions defined by \cite{Yamada2012}.

@@

Figure \ref{fig:distros} shows the spatial distribution for one mock
survey constructed using the {\texttt{match}} method. Each field
corresponds to one of the observational fields. The model parameters
to build it are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. It is only one out of
the $15$ different mock surveys that are constructed for each
model. We note that we use $15\times 12=180$ mock fields out of the
total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed. This restriction makes unable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt{random}} method in order to allow a
fair comparison between the two methods.

@@

The lower limit for the parameter $M_{\rm min}$ is set by the minimum
occupation fraction we are able to consider. At $M_{\rm
  min}=10^{10}$\hMsun the halo number density is already $\sim 10$
times higher than the observational constraints for LAEs. This means
that models in that mass range and an occupation fraction $f_{\rm
  occ}=0.1$ have the possibility to be compatible with observations. Lower
values for $M_{\rm min}$ require $f_{\rm occ}<0.1$, which are not
considered in this \documentname.

For each mock survey generated in a given model ${\mathcal M}$ we
compute the surface density in the $12$ mock fields. We perform a
Kolmogorov-Smirnov (KS) to compare this mock data against the $12$
observational values. From this test we obtain a value $0<P<1$ to
reject the null hypothesis, namely that two data sets come from the
same distribution. In this paper we consider that for values $P>0.05$
the two distributions can be thought as coming from the same
distribution.

We begin by considering that  a model ${\mathcal M}$ that has at least
one mock survey (out of 15) consistent with the observed
distribution of LAE number densities has viable parameters that
deserve to be considered for further analysis. Later on we impose
harder constraints to reduce the number of models by asking that all
the 15 mocks to be consistent with observations.

The second constraint  comes from the angular correlation function (ACF)
for all the models having the $15$ mock surveys consistent with
observations .

{\bf The ACF is computed using  the Landy \&  Szalay estimator
  \citep{Landy1993}  on two different  fields in the mock survey. The
  first field is the densest to be compared against the results of
  \cite{Hayashino2004}. The second field has an average number density and is compared against \cite{Ouchi2010}.}

The observed and mock ACF are fit to a power-law function:
\begin{equation}
\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}, 
\label{eq:fitting}
\end{equation}
where $\theta_0$ and $\beta$ are free parameters. The fit is done
using a least square minimization procedure. For each mock field we obtain a
covariance matrix that gives us the uncertainty in the parameters $\beta$ and
$\theta_0$. Using the $15$ mock fields in a mock survey, we compute a
mean value for the parameters and its associated uncertainty as the
quadratic average of the uncertainties in the fitting procedure. We
consider that a model is consistent with observations if the two
parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$
range.

@@

\bibliographystyle{mn2e}
\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
  et~al.}{2013a}]{Behroozi2013b}
{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013a, \apjl, 762, L31

\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
  et~al.}{2013b}]{Behroozi2013a}
{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013b, \apj, 770, 57

\bibitem[\protect\citeauthoryear{{Colberg}, {White}, {Yoshida}, {MacFarland},
  {Jenkins}, {Frenk}, {Pearce}, {Evrard}, {Couchman}, {Efstathiou}, {Peacock},
  {Thomas} \& {Virgo Consortium}}{{Colberg} et~al.}{2000}]{Colberg00}
{Colberg} J.~M.,  {White} S.~D.~M.,  {Yoshida} N.,  {MacFarland} T.~J.,
  {Jenkins} A.,  {Frenk} C.~S.,  {Pearce} F.~R.,  {Evrard} A.~E.,  {Couchman}
  H.~M.~P.,  {Efstathiou} G.,  {Peacock} J.~A.,  {Thomas} P.~A.,    {Virgo
  Consortium} 2000, \mnras, 319, 209

\bibitem[\protect\citeauthoryear{{Dayal}, {Ferrara}, {Saro}, {Salvaterra},
  {Borgani} \& {Tornatore}}{{Dayal} et~al.}{2009}]{Dayal2009}
{Dayal} P.,  {Ferrara} A.,  {Saro} A.,  {Salvaterra} R.,  {Borgani} S.,
  {Tornatore} L.,  2009, \mnras, 400, 2000

\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Jeeson-Daniel}}{{Dijkstra} \&
  {Jeeson-Daniel}}{2013}]{Dijkstra2013}
{Dijkstra} M.,  {Jeeson-Daniel} A.,  2013, ArXiv e-prints

\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
  {Kramer}}{2012}]{Dijkstra2012}
{Dijkstra} M.,  {Kramer} R.,  2012, \mnras, 424, 1672

\bibitem[\protect\citeauthoryear{{Dijkstra}, {Mesinger} \& {Wyithe}}{{Dijkstra}
  et~al.}{2011}]{Dijkstra11}
{Dijkstra} M.,  {Mesinger} A.,    {Wyithe} J.~S.~B.,  2011, \mnras, 414, 2139

\bibitem[\protect\citeauthoryear{{Forero-Romero} \& {Dijkstra}}{{Forero-Romero}
  \& {Dijkstra}}{2013}]{ForeroRomero2013}
{Forero-Romero} J.~E.,  {Dijkstra} M.,  2013, \mnras, 428, 2163

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero}
  et~al.}{2011}]{ForeroRomero2011}
{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber} \&
  {Prada}}{{Forero-Romero} et~al.}{2012}]{ForeroRomero2012}
{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,    {Prada} F.,  2012,
  \mnras, 419, 952

\bibitem[\protect\citeauthoryear{{Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
  {Verhamme} \& {Hayes}}{{Garel} et~al.}{2012}]{Garel2012}
{Garel} T.,  {Blaizot} J.,  {Guiderdoni} B.,  {Schaerer} D.,  {Verhamme} A.,
  {Hayes} M.,  2012, \mnras, 422, 310

\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio} \&
  {Feldmeier}}{{Gawiser} et~al.}{2007}]{Gawiser2007}
{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
  G.~A.,  {Fazio} G.,    {Feldmeier} J.~J.,  2007, \apj, 671, 278

\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio},
  {Feldmeier}, {Huang}, {Infante}, {Lira} \& {Padilla}}{{Gawiser}
  et~al.}{2007}]{Gawiser07}
{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
  G.~A.,  {Fazio} G.,  {Feldmeier} J.~J.,  {Huang} J.-s.,  {Infante} L.,
  {Lira} P.,    {Padilla} N.,  2007, \apj, 671, 278

\bibitem[\protect\citeauthoryear{{Guaita}, {Francke}, {Gawiser}, {Bauer},
  {Hayes}, {{\"O}stlin} \& {Padilla}}{{Guaita} et~al.}{2013}]{Guaita2013}
{Guaita} L.,  {Francke} H.,  {Gawiser} E.,  {Bauer} F.~E.,  {Hayes} M.,
  {{\"O}stlin} G.,    {Padilla} N.,  2013, \aap, 551, A93

\bibitem[\protect\citeauthoryear{{Hayashino}, {Matsuda}, {Tamura}, {Yamauchi},
  {Yamada}, {Ajiki}, {Fujita}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi},
  {Shimasaku}, {Shioya} \& {Taniguchi}}{{Hayashino}
  et~al.}{2004}]{Hayashino2004}
{Hayashino} T.,  {Matsuda} Y.,  {Tamura} H.,  {Yamauchi} R.,  {Yamada} T.,
  {Ajiki} M.,  {Fujita} S.~S.,  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,
  {Okamura} S.,  {Ouchi} M.,  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,
  2004, \aj, 128, 2073

\bibitem[\protect\citeauthoryear{{Hayes}, {{\"O}stlin}, {Schaerer},
  {Mas-Hesse}, {Leitherer}, {Atek}, {Kunth}, {Verhamme}, {de Barros} \&
  {Melinder}}{{Hayes} et~al.}{2010}]{Hayes2010}
{Hayes} M.,  {{\"O}stlin} G.,  {Schaerer} D.,  {Mas-Hesse} J.~M.,  {Leitherer}
  C.,  {Atek} H.,  {Kunth} D.,  {Verhamme} A.,  {de Barros} S.,    {Melinder}
  J.,  2010, \nat, 464, 562

\bibitem[\protect\citeauthoryear{{Jarosik}, {Bennett}, {Dunkley}, {Gold},
  {Greason}, {Halpern}, {Hill}, {Hinshaw}, {Kogut}, {Komatsu}, {Larson} \&
  {Limon}}{{Jarosik} et~al.}{2011}]{Jarosik2011}
{Jarosik} N.,  {Bennett} C.~L.,  {Dunkley} J.,  {Gold} B.,  {Greason} M.~R.,
  {Halpern} M.,  {Hill} R.~S.,  {Hinshaw} G.,  {Kogut} A.,  {Komatsu} E.,
  {Larson} D.,    {Limon} M.,  2011, \apjs, 192, 14

\bibitem[\protect\citeauthoryear{{Jose}, {Srianand} \& {Subramanian}}{{Jose}
  et~al.}{2013}]{Jose2013b}
{Jose} C.,  {Srianand} R.,    {Subramanian} K.,  2013, ArXiv e-prints

\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
  {Primack}}{{Klypin} et~al.}{2011}]{Bolshoi}
{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102

\bibitem[\protect\citeauthoryear{{Koehler}, {Schuecker} \&
  {Gebhardt}}{{Koehler} et~al.}{2007}]{Koehler2007}
{Koehler} R.~S.,  {Schuecker} P.,    {Gebhardt} K.,  2007, \aap, 462, 7

\bibitem[\protect\citeauthoryear{{Komatsu}, {Dunkley}, {Nolta}, {Bennett},
  {Gold}, {Hinshaw}, {Jarosik}, {Larson}, {Limon}, {Page}, {Spergel} \&
  {Halpern}}{{Komatsu} et~al.}{2009}]{Komatsu2009}
{Komatsu} E.,  {Dunkley} J.,  {Nolta} M.~R.,  {Bennett} C.~L.,  {Gold} B.,
  {Hinshaw} G.,  {Jarosik} N.,  {Larson} D.,  {Limon} M.,  {Page} L.,
  {Spergel} D.~N.,    {Halpern} M.,  2009, \apjs, 180, 330

\bibitem[\protect\citeauthoryear{{Kudritzki}, {M{\'e}ndez}, {Feldmeier},
  {Ciardullo}, {Jacoby}, {Freeman}, {Arnaboldi}, {Capaccioli}, {Gerhard} \&
  {Ford}}{{Kudritzki} et~al.}{2000}]{Kudritzki2000}
{Kudritzki} R.-P.,  {M{\'e}ndez} R.~H.,  {Feldmeier} J.~J.,  {Ciardullo} R.,
  {Jacoby} G.~H.,  {Freeman} K.~C.,  {Arnaboldi} M.,  {Capaccioli} M.,
  {Gerhard} O.,    {Ford} H.~C.,  2000, \apj, 536, 19

\bibitem[\protect\citeauthoryear{{Landy} \& {Szalay}}{{Landy} \&
  {Szalay}}{1993}]{Landy1993}
{Landy} S.~D.,  {Szalay} A.~S.,  1993, \apj, 412, 64

\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
  et~al.}{2013}]{Laursen2013}
{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124

\bibitem[\protect\citeauthoryear{{Laursen}, {Razoumov} \&
  {Sommer-Larsen}}{{Laursen} et~al.}{2009}]{Laursen2009}
{Laursen} P.,  {Razoumov} A.~O.,    {Sommer-Larsen} J.,  2009, \apj, 696, 853

\bibitem[\protect\citeauthoryear{{Laursen} \& {Sommer-Larsen}}{{Laursen} \&
  {Sommer-Larsen}}{2007}]{Laursen2007}
{Laursen} P.,  {Sommer-Larsen} J.,  2007, \apjl, 657, L69

>>>>

Some theoretical attempts to solve this problem using an  ab-initio
approach. They start from the DM halo population to infer the
intrinsic star formation rates and \ly a luminosities. From these
values they estimate the amount of \ly photons that
escape each galaxy and compute the observed luminosity for each
galaxy. These models can predict different observables including: the
luminosity function, correlation function and the equivalent width
distributions. Such modelling has been implemented in semi-analytic
models \citep{Garel2012,Orsi2012,Soler2012} and  full N-body
hydrodynamical simulations \citep{Laursen2007, Dayal2009,
  ForeroRomero2011, Yajima2012}.

These calculations involve many uncertain steps, such as the treatment
of astrophysical processes describing star formation. However, in the
context of LAEs, the dominant uncertainty is the estimation of the
escape fraction, that is the fraction of \ly photons that escape the
galaxy to the observer. Given the resonant nature of the \ly line, the escape
fraction is sensitive to  the dust contents, density, temperature, topology and
kinematics of the neutral Hydrogen in the interstellar medium
(ISM). Solving the radiative transfer of \ly photons in the ISM requires Monte
Carlo simulations. The process of finding a consensus on the expected
value for the \ly escape fraction in high redshift galaxies is still
matter of ongoing research
\citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.

A different approach to infer the typical mass of halos hosting
LAEs is based on the spatial clustering information. This approach uses the fact
that in CDM cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo
mass. Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010}. In these
studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
the conclusions derived on the halo host mass do not delve too deeply
into the possible impact of cosmic variance.

Recently \cite{Yamada2012} observed a wide area of $2.4$ deg$^{2}$
under homogeneous instrumental and data reduction conditions. This data
set is constructed from 12 different sub-fields that allows us to use
clustering statistics and cosmic variance to constraint the mass and
occupation fraction of halos hosting LAEs.

Our method first populates DM halos in cosmological simulations with
LAEs. We only consider whether a DM can host a detectable LAE or not
without predicting a \ly  luminosity. This bypasses all the physical
uncertainties involved in the estimation of observed \ly luminosities.
Once we have the mock LAE catalogs, we compare them against
observations in terms of the  statistics on the number density
distribution derived from the observations over the 12 fields of
\cite{Yamada2012}. We also use measurements of the angular
correlation function to improve these constraints. This method allows
us to constraint the preferred mass range and occupation fraction of DM
halos hosting LAEs.

@@

Our method is based on the comparison of observations and mock
catalogs. We use two different kinds of statistics to perform the
comparison: (i) the distribution of the surface number density
across fields and (ii) the angular correlation function.

In the next subsections we describe in detail the four key
elements int our work-flow. First we present (in two sub-sections) the
observations we take as a benchmark. Second, we describe the main
characteristics of the N-body simulation and the halo catalogs we
use. Third, we recount the important parameters of the simplified
model that we use to populate the halo catalogs with LAEs. Finally, we
describe some of the statistical tests we adopt to compare
observations and mocks .

@@

The primary observational constraint we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey
conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
which has a field of view covering $34\times 27$ arc-min, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
an observed equivalent width, in the observer frame, larger than $190$
\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
sub-fields,  this corresponds to average surface number density of
$0.24\pm 0.01$ arcmin$^{-2}$.

@@

\begin{enumerate}
\item The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
field has been known to harbor a region with a large density excess of
galaxies. {\bf The first sub-field of is taken around the same region
  observed in \cite{Hayashino2004}.}

@@

\item The third  field is the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
$196$ LAEs (1 sub-field), and

@@

{\bf A secondary benchmark is the angular correlation function
(ACF). \cite{Yamada2012} does not report an ACF measurement for
  their fields. Instead we use the results by   \cite{Ouchi2008} who
  reported the ACF is over a region of $1$ deg$^2$ over the SXDS
  field.  We also keep track of the results by \cite{Hayashino2004}
  who reported the ACF in the SSA22 region, including its densest
  subfield.}

{\bf There are some differences between \cite{Ouchi2008} observations
  and those by \cite{Yamada2012}. The details in the color selection,
  corresponding limiting luminosities and EW thresholds are different
  in these references. The average LAEs number density inferred by
  \cite{Hayashino2004} is  $0.37$ arcmin$^{-2}$, which is $30\%$
  higher than the new measurement by \cite{Yamada2012}. In the case of
  \cite{Ouchi2008} the number density is $0.10$ arcmin$^{-2}$, which
  is $\sim 50\%$ lower than the value inferred by \cite{Yamada2012}
  for a portion of the same region.}

@@

{\bf The field SSA22 has been known to harbor a significant
  galaxy overdensity. \cite{Yamada2012} estimates that the densest
  subfield is likely to be a rare density peak with $3-4\sigma$
  significance on the scale of $\sim 60$\hMpc. }

{\bf All the other sub-fields in SSA22 are average. They have a similar
  number density as other blank fields. The left panel in Figure
  \ref{fig:halos} shows the integrated distribution of LAEs number
  density in all the fields reported in  \cite{Yamada2012}. It is
  evident that there is only one sub-field  that stands out as an
  outlier in the distribution (it corresponds to  the densest field in
  SSA22). All the other fields form a continous  distribution in
  number density.}

{\bf Therefore, using the whole SSA22 region as a benchmark in the
  number density distribution does not impose any bias. However, on
  has to  keep in mind that is not plausible that the full number
  density distribution from a simulation will include a very dense
  field. We do not require the presence of such field to judge a mock
  distribution as successful. The statistical test we perform to
  compare mock distributions   against   observations does not require
  such a perfect match.

  In terms of the ACF the results that include the densest
  field in SSA22 \citep{Hayashino2004} are consistent, within 
  uncertainties, with the results of other fields
  \citep{Ouchi2008}. In spite of this consistency we will focus on the
  results from \citep{Ouchi2008}.}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
  method. The larger panel shows $7$ mock
  fields together mimicking the SSA22 region. The intermediate panel
  shows $3$ mock fields corresponding to the SXDS region. The lower
  panels represent the SDF and GOODS-North fields. The same model has
  another 14 associated mock surveys build from different regions in
  the simulation, but constructed following the same pattern.}
\end{center} 
\end{figure*}

We assume that a dark matter halo can only host one
detectable LAE at most.  There are three parameters that
decide whether a halo host a LAE: the lower and upper bounds for the
mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
must keep in mind that the physical interpretation of the occupation
fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
forming galaxy in a halo and its detectability as a LAE.

{\bf We recall that we do not perform a explicit modeling for LAE
detectability. Our model does not assign a luminosity or escape
fraction for each LAE. We are interested in constraining the halo
mass range hosting detectable LAEs commonly used in photometric
narrow-band surveys. We also want to explore a wide range of
possible masses for the host halos without any strong theoretical
prejudice regarding the details of star formation in high-redshift
galaxies. }

@@

Figure \ref{fig:distros} shows the spatial distribution for one mock
survey constructed using the {\texttt{match}} method. Each field
corresponds to one of the observational fields. The model parameters
to build the mock are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. The figure shows only
one out of the $15$ different mock surveys that are constructed for
each model. We note that we only use $15\times 12=180$ mock fields out of the
total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed. This restriction makes unable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt{random}} method in order to allow a
fair comparison between the two methods.

@@

The lower limit for the parameter $M_{\rm min}$ is set by the minimum
occupation fraction we decide to consider. At $M_{\rm
  min}=10^{10}$\hMsun the halo number density around that mass range
is $\sim 10$ times higher than the observational constraints
for LAEs. This means that models in that mass range and an occupation fraction $f_{\rm  occ}=0.1$ have the possibility to be compatible with
observations. Lower values for $M_{\rm min}$ require $f_{\rm
  occ}<0.1$, which are not considered in this \documentname.  {\bf In
  turn exploring occupation fractions on the order of $f_{\rm occ}=0.01$ requires
  only makes sense for halo populations in the mass range of
  $10^{9}$\hMsun which are abundant enough to fit observations with a
  low occupation fraction. In our case that mass range is not resolved
  by the Bolshoi simulation an are not considered here.}

For each mock survey generated in a given model ${\mathcal M}$ we
compute the surface density in its $12$ mock fields. We perform a
Kolmogorov-Smirnov (KS) to compare these values against the $12$
observational values. This tests gives us a value $0<P<1$ to
reject the null hypothesis, namely that two data sets come from the
same distribution. In this paper we consider that for values $P>0.05$
the two distributions can be thought as coming from the same
distribution.

We begin by considering that  a model ${\mathcal M}$ with at least one
mock survey (out of 15) consistent with observations has viable
parameters to host LAEs. From that we consider a stronger constraints
to reduce the number of models by asking that all the 15 mocks to be
consistent with observations and analyze again the properties of the
resulting models. Finally we add the ACF as an additional constraint
and consider all the models having their $15$ mocks consistent with
observations.

{\bf The ACF is computed using  the Landy \&  Szalay estimator
  \citep{Landy1993}  on fields of size $1$ deg$^2$ to be compared
  against the results reported by \cite{Ouchi2010}.}

The observed and mock ACF are fit to a power-law function:
\begin{equation}
\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}, 
\label{eq:fitting}
\end{equation}
where $\theta_0$ and $\beta$ are free parameters. The fit is done
using a least square minimization procedure. For each mock field we
obtain a covariance matrix that gives us the uncertainty in the
parameters $\beta$ and $\theta_0$. {\bf We consider that a mock field is
consistent with observations if the two parameters $\beta$ and
$\theta_0$ are equal within a $1$-$\sigma$ range.}

@@

\bibliographystyle{mn2e}
\bibliography{references}
